---
title: "Meta-analysis of iAs BC"
author: "Zheng Zhou"
date: "5/13/2019"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

# Introduction

The objective of our meta-analysis is to have a robust, distributional estimation of the bioaccessibility (BC)
of inorganic arsenic in rice.
We first simulated bioaccessibility values for 1000 iterations using a boostrapping, parametric simulation techinque
[Rubinstein & Kroese, 2016][1] based on summarized original data as shown in table S1.
Each iteration of the simulated bioaccessibility data were then analyzed with the Maximum Likelihood Estimate
algorithm [Cramér,H.,2016][2] to estimate a pair of beta parameters.
The 1000 pairs of beta parameters were summarized and plotted for visualization. We took the mean curve to 
describe the central tendency of the data, which is marked in red.

# Procedure

## Load original data and cleaning

Load the data:
```{r}
library(readxl)
AsBC <- read_excel("Study summary 0517.xlsx" , sheet = "iAs BC")
```

Dissect the dataset by study:
```{r}
# only intestine data are used
# Sun et al. 2012, Alava et al. 2013b and the last two sample of Calatayud et al. 2018 are not used

# Ackernman et al. 2005
Ackerman <- AsBC[1:5,]
nAck <- 5

# Laparra et al. 2005
Laparra <- AsBC[6:13,]
nLap <- 8

# Alava et al. 2013a
AlavaA <- AsBC[18:20,]
nAlaA <- 3

# Lee et al. 2018
Lee <- AsBC[24:33,]
nLee <- 10

# Calatayud et al. 2018
Cala <- AsBC[34:35,]
nCala <- 2
```

If the study provides detailed data of each sample in the study, then the sample-wise data are used for simulation;
otherwise the across-sample, study-summary data are used.
Taking [Alava et al.(2013)a][4] as an example. 

```{r}
print(AlavaA)
```

The study reports bioaccessibility values for each of its three samples. Therefore, the three bioaccessibility
values were simulated. 

For each study, the number of data simulated depends on the sample size of the study and number of replicates in
each sample. Still taking [Alava et al.(2013)a][4] as an example, it has three samples with three replicates in
each sample. Therefore, a total of nine data points were simulated for this study.

Concentrations are simulated based on the assumption of normality, same as the weighted average method.
Bioaccessibility is simulated based on the assumption of uniform distribution, if the mean+2SD of bioaccessibility
would exceed 100%.

Define a function to simulate data for a study given sample size, number of replicate in each sample, mean and SD
of each sample:
```{r}
muSDGen <- function(s,r,mu,sd){                   # s sample size, r replicate, mu mean, sd SD
  temp <- list()
  y <- vector()
  for (i in 1:s){                                 # for each sample, simulate data points = number of replicates
    temp[[i]] <- rnorm(r[i],mu[i],sd[i])          # assumption of normal distribution for arsenic concentration
    y <- c(y, unlist(temp[i]))
  }
 return(y)                                       # put all simulated values in one vector
}
iter <- 1000                    # number of iteration
set.seed(47401)                 # set a random seed to start
```

If bioaccessibility values were reported in the study, bioaccessibility was simulated directly from reported values.
If bioaccessibility values were not reported, bioaccessibility data were computed based on the definition of 
bioaccessibility:
$$
Bioaccessibility  = \frac{M_{bioaccessible}}{M_{original}} \\
where\, M_{bioaccessible}=amount/concentration\,of\,inorganic\,arsenic\,that\,is\,soluble\,in\,GI\,tract \\
       M_{original}=amount/concentration\,of\,inorganic\,arsenic\,that\,is\,soluble\,in\,rice
$$
For example, [Ackerman et al.(2005)][3] does not report bioaccessibility values directly. The mean$\pm{SD}$ of
concentration of iAs in cooked rice and the bioaccessible concentration in GI extracts were available instead.
Concentrations were simulated following the procedure described previously and bioaccessibility was calculated using
the equation above.

## Simulation of iAs BC

Simulated bioaccessibility data in one iteration are pooled together.
Number of data in one simulate = sum of replicates in all studies.

Parameters of beta distributions (a,b) are estimated by the data in each iteration. Since the data were simulated
for 1000 iterations, there are 1000 pairs of parameters. 
A beta curve is plotted using each pair of parameters. A graph of the 1000 curve is displayed.

Ackerman et al. 2005 : sample-wise BC is reported as mean and SD, would not exceed 100%
```{r}
sim.mtx.ack <- matrix(NA,iter, sum(Ackerman$replicate))
for ( i in 1:iter) {
  temp.ack <- muSDGen( s = nAck,
           r = Ackerman$replicate,
           mu = Ackerman$`iAs post_mean`,                 # post iAs
           sd = Ackerman$`iAs post_sd`) /  
    muSDGen( s = nAck,
             r = Ackerman$replicate,
             mu = Ackerman$`iAs pre_mean`,                # pre iAs
             sd = Ackerman$`iAs pre_sd`)
   if (sum(temp.ack >= 1) == 0) {
     sim.mtx.ack[i,] <- temp.ack
   } else {
     while( sum(temp.ack >= 1) != 0){
       temp.ack <- muSDGen( s = nAck,
                        r = Ackerman$replicate,
                        mu = Ackerman$`iAs post_mean`,                 # post iAs
                        sd = Ackerman$`iAs post_sd`) /  
         muSDGen( s = nAck,
                  r = Ackerman$replicate,
                  mu = Ackerman$`iAs pre_mean`,                # pre iAs
                  sd = Ackerman$`iAs pre_sd`)
     }
     sim.mtx.ack[i,] <- temp.ack
   }
}
```

Laparra et al. 2005: sample-wise BC not reported; sample-wise iAs concentrations were reported. However, simulated
bioaccessibility in most samples based on normal distriubtion of concentrations exceeded 100%.
Use an uniformly distributed across-sample bioaccessibility of 63-99% as reported by the author.
```{r}
sim.mtx.lap <- matrix(NA,iter,sum(Laparra$replicate))
for( i in 1:iter){
  sim.mtx.lap[i,] <- runif(sum(Laparra$replicate),0.63,0.99)
}
```

Alava et al. 2013a: sample-wise BC reported as mean and SD, would not exceed 100%
```{r}
sim.mtx.alaA <- matrix(NA,iter, sum(AlavaA$replicate))
for ( i in 1:iter) {
   temp.alaA <- rnorm(AlavaA$replicate,AlavaA$`iAs BC_mean`,AlavaA$`iAs BC_sd`)
   if (sum(temp.alaA >= 1) == 0) {
     sim.mtx.alaA[i,] <- temp.alaA
   } else {
     while(sum(temp.alaA >= 1) != 0){
       temp.alaA <- rnorm(AlavaA$replicate,AlavaA$`iAs BC_mean`,AlavaA$`iAs BC_sd`)
     }
   sim.mtx.alaA[i,] <- temp.alaA
   }
}
```

Lee et al. 2018: BC not reported; sample-wise concentration available, would not exceed 100%
```{r}
sim.mtx.lee <- matrix(NA,iter, sum(Lee$replicate))
for( i in 1:iter) {
    temp.lee <- muSDGen( s = nLee,
           r = Lee$replicate,
           mu = Lee$`iAs post_mean`,      # post iAs
           sd = Lee$`iAs post_sd`) / 
    muSDGen( s = nLee,
             r = Lee$replicate,
             mu = Lee$`iAs pre_mean`,     # pre iAs
             sd = Lee$`iAs pre_sd`)
    if (sum(temp.lee >= 1) == 0) {
      sim.mtx.lee[i,] <- temp.lee
    } else {
      while( sum(temp.lee >= 1) != 0){
        temp.lee <- muSDGen( s = nLee,
                         r = Lee$replicate,
                         mu = Lee$`iAs post_mean`,      # post iAs
                         sd = Lee$`iAs post_sd`) / 
          muSDGen( s = nLee,
                   r = Lee$replicate,
                   mu = Lee$`iAs pre_mean`,     # pre iAs
                   sd = Lee$`iAs pre_sd`)
      }
      sim.mtx.lee[i,] <- temp.lee
    }
}
```

Calatayud et al. 2018: sample-wise BC reported as single value. Uniform distribution applied (0.86,1) as across-
sample data
```{r}
sim.mtx.cala <- matrix(NA,iter,sum(Cala$replicate))
for( i in 1:iter){
  sim.mtx.cala[i,] <- runif(sum(Cala$replicate),0.86,0.99)
}
```

## MLE estimate and plotting of iAs BC

```{r}
library(Rfast)
iAsBC <- matrix(NA,iter,84)
beta.para<-matrix(NA,iter,2)
for (i in 1:iter){
  iAsBC[i,]<-c(sim.mtx.ack[i,],
                 sim.mtx.lap[i,],
                 sim.mtx.alaA[i,], 
                 sim.mtx.lee[i,],
                 sim.mtx.cala[i,])
  sample.temp <- iAsBC[i,]
  beta.para[i,]<-beta.mle(sample.temp)$param  
}

## Get plot for the Beta Distributions ##
plot.step<-seq(0,1,length.out = 501)
plot.resp.mtx<-matrix(NA,iter,length(plot.step))

plot(0, 0, ty = "n", xlab="Intestinal Bioaccessibility of Inorganic Arsenic in Rice",ylab="Density", 
     main="Estimated Distribution of Bioaccessibility",xlim = c(0,1), ylim=c(0,8),
     cex.axis=1.3, cex.lab=1.3, cex.main=1.3)
for (i in 1:iter){
  plot.resp.mtx[i,]<-dbeta(plot.step,beta.para[i,1],beta.para[i,2])
  lines(plot.step,plot.resp.mtx[i,],col="grey")
}
mean.curve<-colMeans(plot.resp.mtx)
lines(plot.step,mean.curve,col="red")
# find parameters of the estimated mean curve
a1 <- mean(beta.para[,1])
b1 <- mean(beta.para[,2])
guess <- dbeta(plot.step,a1,b1)
lines(plot.step,guess,col="blue")
```

## simulation of tAs BC

The simulation was performed by study. We employed the same method as we used in the simulation of iAs
bioaccessibility. Additionally, we ensured that assumptions of simulation were consistent within each study.
That is, if sample-wise simulation was perfromed for iAs bioaccessibility, it will also be carried out for all
other simulations of this study.

Ackerman et al. 2005: sample-wise tAs bioaccessibility was provided in the paper.
We perfromed sample-wise simulate for tAs bioaccessibility, using the same procedure as for iAs bioaccessibility.
However, one sample reports value > 100%. We used an approximate of 0.999 for this sample.
```{r}
sim.tBC.ack <- matrix(NA,iter, sum(Ackerman$replicate))
for ( i in 1:iter) {
  temp <- c(rnorm(3,0.97,0.0185), # normality assumed if value no greater than 100%
            rnorm(3,0.92,0.0085), 
            rep(0.999,times = 3),  # mean >> 1, simulated as 0.999
            rnorm(3,0.8,0.0055),
            rnorm(5,0.95,0.0295))
  if (sum(temp>1) ==0){
    sim.tBC.ack[i,] <- temp
  } else {
    while(sum(temp>1) !=0){
            temp <- c(rnorm(3,0.97,0.0185), # normality assumed if value no greater than 100%
            rnorm(3,0.92,0.0085), 
            rep(0.999,times = 3),  # mean >> 1, simulated as 0.999
                  rnorm(3,0.8,0.0055),
                  rnorm(5,0.95,0.0295))
    }
    sim.tBC.ack[i,] <- temp
  }
}
```

Laparra et al. 2005: across-sample: tAs bioaccessibility not reported by the author. We used the mean tAs
bioaccessibiliy 0.834-1.000 as shown in table 1 following a across-sample uniform distribution for simulation.
```{r}
sim.tBC.lap <- matrix(NA,iter,sum(Laparra$replicate))
for(i in 1:iter){
  sim.tBC.lap[i,] <- runif(sum(Laparra$replicate),0.834,0.999)
}
```

Sun et al.2012: this study did not enable us to simulate its iAs bioaccessibility data, we did not include it in
our regression.

Alava et al. 2013a:tAs bioaccessibility was simulated based on data on arsenic speication in cooked rice and the 
bioaccessibility of iAs and oAs respectively. 
Bioaccessible tAs was estimated = iAs bioaccessibility * iAs concentration in rice + oAs bioaccessibility * 
oAs concentration in rice.
tAs bioaccessibility was then estimated = bioaccessible tAs / tAs concentration in rice.
```{r}
sim.tBC.alaA <- matrix(NA, iter, sum(AlavaA$replicate))
for(i in 1:iter){
  tAs.bio <- sim.mtx.alaA[i,] * (muSDGen(s = nAlaA, r = AlavaA$replicate,   # iAs BC * (iAs pre = AsIII pre+
          mu = AlavaA$`AsIII pre_mean` , sd = AlavaA$`AsIII pre_sd`) + 
            muSDGen(s = nAlaA, r = AlavaA$replicate,                          # AsV pre)
                    mu = AlavaA$`AsV pre_mean` , sd = AlavaA$`AsV pre_sd`))+ 
          muSDGen(s = nAlaA, r = AlavaA$replicate,                        # oAs BC * oAs pre
                  mu = AlavaA$`oAs BC_mean` , sd = AlavaA$`oAs BC_sd`)*
          muSDGen(s = nAlaA, r = AlavaA$replicate, mu = AlavaA$`oAs pre_mean` , sd = AlavaA$`oAs pre_sd`)
  sim.tBC.alaA[i,] <- tAs.bio / muSDGen(s = nAlaA, r = AlavaA$replicate,    # tAs BC = tAs bio / 
                                mu = AlavaA$`tAs pre_mean` , sd = AlavaA$`tAs pre_sd`) # tAs pre
}
```

Lee et al.2018: this study provides sample-wise tAs concentration data.
```{r}
sim.tBC.lee <- matrix(NA,iter, sum(Lee$replicate))
for( i in 1:iter) {
    temp.lee <- muSDGen( s = nLee,
           r = Lee$replicate,
           mu = Lee$`tAs post_mean`,              # post tAs
           sd = Lee$`tAs post_sd`) / 
    muSDGen( s = nLee,
             r = Lee$replicate,
             mu = Lee$`tAs pre_mean`,             # pre tAs
             sd = Lee$`tAs pre_sd`)
    if (sum(temp.lee >= 1) == 0) {
      sim.tBC.lee[i,] <- temp.lee
    } else {
      while( sum(temp.lee >= 1) != 0){
            temp.lee <- muSDGen( s = nLee,
                r = Lee$replicate,
                mu = Lee$`tAs post_mean`,              # post tAs
                sd = Lee$`tAs post_sd`) / 
              muSDGen( s = nLee,
                r = Lee$replicate,
                mu = Lee$`tAs pre_mean`,             # pre tAs
                sd = Lee$`tAs pre_sd`)
      }
      sim.tBC.lee[i,] <- temp.lee
    }
}
```

Calatayud et al. 2018: across-sample simulation is performed for tAs bioaccessibility same as for iAs.
We used a mean tAs bioaccessbility value of 0.854-1.000 following uniform distribution as shown in table 1.
```{r}
sim.tBC.cala <- matrix(NA,nrow = iter, ncol = sum(Cala$replicate))
for(i in 1:iter){
  sim.tBC.cala[i,] <- runif(sum(Cala$replicate),0.854,0.999)
}
```

## MLE estimation of tAs BC

The distribution of tAs BC was estimated and plotted using the same method as for iAs BC. i
A beta distribution is assumed for tAs BC because its range falls within (0,1), which best accomendates our data of
tAs BC compared with other distributions. 
The two parameters of beta distribution, a and b, were estimated by iteration. 
Therefore, 1000 pairs of a and b were estimated from 1000 iterations of tAs BC data.

```{r}
tAsBC <- matrix(NA,iter,84)
beta.para.tAs<-matrix(NA,iter,2)
for (i in 1:iter){
  tAsBC[i,]<-c(sim.tBC.ack[i,],
                 sim.tBC.lap[i,],
                 sim.tBC.alaA[i,], 
                 sim.tBC.lee[i,],
                 sim.tBC.cala[i,])
  sample.temp.tAs <- tAsBC[i,]
  beta.para.tAs[i,]<-beta.mle(sample.temp.tAs)$param  
}

## Get plot for the Beta Distributions ##
plot.step<-seq(0,1,length.out = 501)
plot.tAs.mtx<-matrix(NA,iter,length(plot.step))

plot(0, 0, ty = "n", xlab="Intestinal Bioaccessibility of Total Arsenic in Rice",ylab="Density", 
     main="Estimated Distribution of Bioaccessibility",xlim = c(0,1), ylim=c(0,8),
     cex.axis=1.3, cex.lab=1.3, cex.main=1.3)
for (i in 1:iter){
  plot.tAs.mtx[i,]<-dbeta(plot.step,beta.para.tAs[i,1],beta.para.tAs[i,2])
  lines(plot.step,plot.tAs.mtx[i,],col="grey")
}
mean.curve.tAs<-colMeans(plot.tAs.mtx)
lines(plot.step,guess.tAs , col = "blue", lwd = 2)

# find the parameter of the mean curve
a2 <- mean(beta.para.tAs[,1])    # mean of estimated parameters
b2 <- mean(beta.para.tAs[,2])
guess.tAs <- dbeta(plot.step,a2,b2)
lines(plot.step,guess.tAs , col = "red")
```

## Correlation between iAs BC and tAs BC

We studied the correlation between iAs BC and tAs BC. 
We applied Pearson's Product-Moment Correlation Coefficient method to estimate the linear correlation between 
iAs BC and tAs BC [Cramér,H.,2016][2].
This estimation was based on data drawn from studies where both iAs BC and tAs BC are available.
```{r}
# iAs BC and tAs BC have the same number of iterations
# these data construct 1000 iterations of iAs BC- tAs BC pairs.
# estimate Pearson's r for data in each iteration
library(Hmisc) # function to return both r and p
cor.mtx <- matrix(NA,iter,2)            # a matrix to keep r and p
colnames(cor.mtx) <- c("Pearson'r" , "p value")
cor.list <- list()    # create a list to keep estimated correlation output
for( i in 1:iter){                             
  cor.list[[i]] <- rcorr(iAsBC[i,],tAsBC[i,])             # calculate r and p
  cor.mtx[i,1] <-  cor.list[[i]]$r[1,2]          # keep Pearson's r in the first column
  cor.mtx[i,2] <- cor.list[[i]]$P[1,2]
}
summary(cor.mtx[,1])
hist(cor.mtx[,1] , main = "Pearson's r between iAs BC and tAs BC" , xlab = "Pearson'r")
# number of r that are significant
sum(cor.mtx[,2] < .05)
```
Our results show that the correlation between iAs BC and tAs BC is weak (mean r = -0.21) . 51.4% of the p value is
less than 0.05, indicating that the significance of r might completely result from randomness. 

## Regression Analysis

To study the association between factors that might affect iAs bioaccessibility, we applied a generlized linear
model to identify factors having strong correlation with iAs bioaccessibility.
Since our dependent varaible is a continous variable of value in [0,1]. We applied a normal error distribution
with logit inverse link function in our regression analysis.

The predictors included in our regression analysis are: 
concentration of inorganic arsenic in cooking water ug/L (iAs cooking),milling status of rice(milling),
and rice grain type(grain).


```{r}
# create vectors to keep cooking, milling and grain
cooking <- c(rep(Ackerman$`iAs cooking`,times = Ackerman$replicate),
             rep(Laparra$`iAs cooking`,times = Laparra$replicate),
             rep(AlavaA$`iAs cooking`,times = AlavaA$replicate),
             rep(Lee$`iAs cooking`,times = Lee$replicate),
             rep(Cala$`iAs cooking`,times = Cala$replicate))
milling <- c(rep(Ackerman$milling,times = Ackerman$replicate),
             rep(Laparra$milling,times = Laparra$replicate),
             rep(AlavaA$milling,times = AlavaA$replicate),
             rep(Lee$milling,times = Lee$replicate),
             rep(Cala$milling,times = Cala$replicate))
grain <- c(rep(Ackerman$grain,times = Ackerman$replicate),
             rep(Laparra$grain,times = Laparra$replicate),
             rep(AlavaA$grain,times = AlavaA$replicate),
             rep(Lee$grain,times = Lee$replicate),
             rep(Cala$grain,times = Cala$replicate))
# first fit a linear regression model with logit inverse link function
mod.list <- list()
for(i in 1:iter){
  mod0 <- lm(iAsBC[i,] ~ cooking+milling+grain,
                      family=gaussian(link = "logit") , na.action = na.omit)
  mod.list[[i]] <- summary(mod0)
}
# keep fitted coefficient, SE and p value for each predictor 
mod.coef <- matrix(NA,iter,5)
mod.SE <- matrix(NA,iter,5)
mod.p <- matrix(NA,iter,5)
mod.mtx <- matrix(NA,iter,17)
rsqrd <- vector()
p <- vector()
for(i in 1:iter){
  mod.coef[i,] <- mod.list[[i]]$coefficients[,1]  # estimated coefficient
  mod.SE[i,] <- mod.list[[i]]$coefficients[,2] # SE
  mod.p[i,] <- mod.list[[i]]$coefficients[,4] # p value of predictors
  rsqrd [i] <- mod.list[[i]]["r.squared"]         # r square
  Fstat <- unlist(mod.list[[i]]["fstatistic"])
  attributes(Fstat) <- NULL
  p[i] <- pf(Fstat[1],Fstat[2],Fstat[3],lower.tail = F)   # use F stats to calculate model p value
}


mod.mtx <- matrix(NA,iter,17)
for(i in 1:iter){
  mod.mtx[i,1:5] <- mod.list[[i]]$coefficients[,1]  # estimated coefficient
  mod.mtx[i,6:10] <- mod.list[[i]]$coefficients[,2] # SE
  mod.mtx[i,11:15] <- mod.list[[i]]$coefficients[,4] # p value of predictors
  mod.mtx[i,16] <- mod.list[[i]]["r.squared"]         # r square
  Fstat <- unlist(mod.list[[i]]["fstatistic"])
  attributes(Fstat) <- NULL
  mod.mtx[i,17] <- pf(Fstat[1],Fstat[2],Fstat[3],lower.tail = F)   # use F stats to calculate model p value
}
```


### Prediction of iAs BC from tAs BC 

As indicated in the results of our correlation test, the association between iAs BC and tAs BC are weak and not
very likely to be significant. 
We perfromed a regression analysis to predict iAs BC from tAs BC using a simple linear model.
Both iAs BC and tAs BC are on the percentage scale.
```{r}
reg.list <- list()   # a list to keep regression output
for( i in 1:iter){                             
  iAsBC <- c(sim.mtx.ack[i,],
              sim.mtx.lap[i,],
              sim.mtx.alaA[i,], 
              sim.mtx.lee[i,],
              sim.mtx.cala[i,])
  tAsBC <- c(sim.tBC.ack[i,],
             sim.tBC.lap[i,],
             sim.tBC.alaA[i,],
             sim.tBC.lee[i,],
             sim.tBC.cala[i,])
  reg.list[[i]] <- lm(iAsBC ~ tAsBC)
  reg.coef[i] <- reg.list[[i]]$coefficients[2]    # keep the coefficient in the first column
}
# inspect coefficient and p value
summary(reg.coef)
hist(reg.coef , main = "Regression Coefficient" , xlab = "Regression coefficient of tAs BC on iAs BC")
```

# Reference

[1]:Rubinstein, R. Y., & Kroese, D. P. (2016). Simulation and the Monte Carlo method (Vol. 10): John Wiley & Sons.

[2]:Cramér, H. (2016). Mathematical methods of statistics (PMS-9) (Vol. 9): Princeton university press.

[3]:Ackerman, A. H., Creed, P. A., Parks, A. N., Fricke, M. W., Schwegel, C. A., Creed, J. T., . . . Velal, N. P.
(2005). Comparison of a chemical and enzymatic extraction of arsenic from rice and an assessment of the arsenic
absorption from contaminated water by cooked rice. Environ Sci Technol, 39(14), 5241-5246.

[4]:Alava, P., Du Laing, G., Odhiambo, M., Verliefde, A., Tack, F., & Van de Wiele, T. R. (2013)a. Arsenic
bioaccessibility upon gastrointestinal digestion is highly determined by its speciation and lipid-bile salt
interactions. Journal of Environmental Science and Health, Part A, 48(6), 656-665.

[5]:Alava, P., Tack, F., Laing, G. D., & Van de Wiele, T. (2013)b. Arsenic undergoes significant speciation changes
upon incubation of contaminated rice with human colon micro biota. J Hazard Mater, 262, 1237-1244. 

[6]:Calatayud, M., Xiong, C., Du Laing, G., Raber, G., Francesconi, K., & van de Wiele, T. (2018). Salivary and Gut
Microbiomes Play a Significant Role in in Vitro Oral Bioaccessibility, Biotransformation, and Intestinal Absorption 
of Arsenic from Food. Environ Sci Technol, 52(24), 14422-14435. 

[7]:Laparra, J. M., Velez, D., Barbera, R., Farre, R., & Montoro, R. (2005). Bioavailability of inorganic arsenic
in cooked rice: practical aspects for human health risk assessments. J Agric Food Chem, 53(22), 8829-8833.

[8]:Lee, S. G., Kim, J., Park, H., Holzapfel, W., & Lee, K. W. (2018). Assessment of the effect of cooking on
speciation and bioaccessibility/cellular uptake of arsenic in rice, using in vitro digestion and Caco-2 and PSI
cells as model. Food Chem Toxicol, 111, 597-604. 

[9]:Sun, G. X., Van de Wiele, T., Alava, P., Tack, F., & Du Laing, G. (2012). Arsenic in cooked rice: effect of
chemical, enzymatic and microbial processes on bioaccessibility and speciation in the human gastrointestinal
tract. Environ Pollut, 162, 241-246.