---
title: "iAs BC fitting"
author: "Zheng Zhou"
date: "7/30/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction and Objectives   

In this document, I will explain three things:  
1. why the ML estimate of beta is considered as a poor fit judging by KS statistics    
2. What I propose to solve the problem     

Please make direct references to specific scripts where you believe I made mistakes.   

# 1 Simulation   

***I assure you that my literature search is complete***   
***I assure you that there is no errors in my simulation***   

I present the script of data simulation just in case. If you don't have patience, please skip to the next section.

```{r}
library(readxl)
iter <- 1000
set.seed(47405)

## =======load data======
ASBC <- read_xlsx("Study summary 0708.xlsx",
                  sheet = "iAs BC")
head(ASBC)                                       # inspect the top lines

## -----simulation function-----
muSDGen <- function(s,r,mu,sd){                   # s sample size, r replicate, mu mean, sd SD
  temp <- list()
  y <- vector()
  for (i in 1:s){                                 # for each sample, simulate data points = number of replicates
    temp[[i]] <- rnorm(r[i],mu[i],sd[i])          # assumption of normal distribution for arsenic concentration
    y <- c(y, unlist(temp[i]))
  }
  return(y)                                       # put all simulated values in one vector
}

## ----------
# study 1 ackerman 2005

## iAsBC not reported;
## iAsBC = iAs_post/iAs_pre

nrow.ack <- which(ASBC$Ref == "Ackerman et al. 2005")
ackerman <- ASBC[nrow.ack,]
n.ack <- length(nrow.ack)
dup.ack <- ackerman$replicate

ias.pre.mu.ack <- ackerman$`iAs pre_mean`
ias.pre.sd.ack <- ackerman$`iAs pre_sd`
oas.pre.mu.ack <- ackerman$`oAs pre_mean`
oas.pre.sd.ack <- ackerman$`oAs pre_sd`
tas.pre.mu.ack <- ackerman$`tAs pre_mean`
ias.post.mu.ack <- ackerman$`iAs post_mean`
ias.post.sd.ack <- ackerman$`iAs post_sd`
oas.post.mu.ack <- ackerman$`oAs post_mean`
oas.post.sd.ack <- ackerman$`oAs post_sd`
tas.post.mu.ack <- ackerman$`tAs post_mean`
tas.post.sd.ack <- ackerman$`tAs post_sd`
tbc.mu.ack <- ackerman$`tAs BC_mean`
tbc.sd.ack <- ackerman$`tAs BC_sd`

upper.ack<-0.999999
lower.ack<-0

sim.ias.pre.ack <- matrix(NA,iter,sum(dup.ack))
sim.ibc.ack <- matrix(NA,iter,sum(dup.ack))
sim.obc.ack <- matrix(NA,iter,sum(dup.ack))
sim.prp.ack <- matrix(NA,iter,sum(dup.ack))
sim.tbc.ack <- matrix(NA,iter,sum(dup.ack))

for(i in 1:iter){
  temp.post.ack <- muSDGen(s=n.ack, # iAs post
                           r=dup.ack,
                           mu=ias.post.mu.ack,
                           sd=ias.post.sd.ack)
  temp.iAs.pre.ack <- muSDGen(s=n.ack,  # iAs pre
                              r=dup.ack,
                              mu=ias.pre.mu.ack,
                              sd=ias.pre.sd.ack)
  sim.ias.pre.ack[i,] <- temp.iAs.pre.ack   # iAs pre in matrix for regression
  
  temp.iBC.ack <- temp.post.ack/temp.iAs.pre.ack  # iAs BC
  temp.iBC.ack[temp.iBC.ack>upper.ack]<-upper.ack  # iBC truncation
  temp.iBC.ack[temp.iBC.ack<lower.ack]<-lower.ack
  sim.ibc.ack[i,]<-temp.iBC.ack
  
  temp.tBC.ack <- muSDGen(s=n.ack,                  # tBC
                          r=dup.ack,
                          mu=tbc.mu.ack,
                          sd=tbc.sd.ack)
  temp.tBC.ack[temp.tBC.ack > upper.ack] <- upper.ack       # tBC truncation
  temp.tBC.ack[temp.tBC.ack < lower.ack] <- lower.ack
  sim.tbc.ack[i,] <- temp.tBC.ack
  
  temp.prp.ack <- temp.iAs.pre.ack / rep(tas.pre.mu.ack,times=dup.ack) # iAs proportion
  
  sim.prp.ack[i,]<-temp.prp.ack     # iAs prp in matrix for regression
  
  temp.oas.pre.ack <- muSDGen(s=n.ack,                          # oAs pre
                              r=dup.ack,
                              mu=oas.pre.mu.ack,
                              sd=oas.pre.sd.ack)
  temp.oas.post.ack <- muSDGen(s=n.ack,                          # oAs post
                              r=dup.ack,
                              mu=oas.post.mu.ack,
                              sd=oas.post.sd.ack)
  temp.obc.ack <- temp.oas.post.ack / temp.oas.pre.ack        # oBC
  temp.obc.ack[temp.obc.ack>upper.ack]<-upper.ack  # oBC truncation
  temp.obc.ack[temp.obc.ack<lower.ack]<-lower.ack
  sim.obc.ack[i,] <- temp.obc.ack
}

## ----------
## study 2: alava 2013a

## iAsBC reported as mean and SD
# iAs_pre=iAs3 + iAs5
# tAs BC = (iAs pre * iBC + oAs pre * oBC) / tAs pre

nrow.ala13 <- which(ASBC$Ref == "Alava et al. 2013a")
alava13 <- ASBC[nrow.ala13,]
n.ala13 <- length(nrow.ala13)
dup.ala13 <- alava13$replicate

ibc.mu.ala13 <- alava13$`iAs BC_mean`
ibc.sd.ala13 <- alava13$`iAs BC_sd`
as3.pre.mu.ala13 <- alava13$`AsIII pre_mean`
as3.pre.sd.ala13 <- alava13$`AsIII pre_sd`
as5.pre.mu.ala13 <- alava13$`AsV pre_mean`
as5.pre.sd.ala13 <- alava13$`AsV pre_sd`
oas.pre.mu.ala13 <- alava13$`oAs pre_mean`
oas.pre.sd.ala13 <- alava13$`oAs pre_sd`
tas.pre.mu.ala13 <- alava13$`tAs pre_mean`
tas.pre.sd.ala13 <- alava13$`tAs pre_sd`
obc.mu.ala13 <- alava13$`oAs BC_mean`
obc.sd.ala13 <- alava13$`oAs BC_sd`

upper.ala<-0.999999
lower.ala<-0

sim.ibc.ala13 <- matrix(NA,iter,sum(dup.ala13))
sim.ias.pre.ala13 <- matrix(NA,iter,sum(dup.ala13))
sim.prp.ala13 <- matrix(NA,iter,sum(dup.ala13))
sim.obc.ala13 <- matrix(NA,iter,sum(dup.ala13))
sim.tbc.ala13 <- matrix(NA,iter,sum(dup.ala13))

for(i in 1:iter){
  temp.iBC.ala <- muSDGen(s= n.ala13,                        # iAs BC
                          r= dup.ala13,
                          mu=ibc.mu.ala13,
                          sd=ibc.sd.ala13)
  temp.iBC.ala[temp.iBC.ala > upper.ala] <- upper.ala        # iBC truncation
  temp.iBC.ala[temp.iBC.ala] <- lower.ala
  sim.ibc.ala13[i,] <- temp.iBC.ala
  
  temp.iAs.pre.ala <- muSDGen(n.ala13,                        # iAs pre=3+5
                              dup.ala13,
                              as3.pre.mu.ala13,
                              as3.pre.sd.ala13)+
    muSDGen(n.ala13,                        
            dup.ala13,
            as5.pre.mu.ala13,
            as5.pre.sd.ala13)
  sim.ias.pre.ala13[i,] <-temp.iAs.pre.ala
  
  temp.iAs.post.ala <- temp.iBC.ala * temp.iAs.pre.ala        # iAs post = iBC*iAs pre
  
  temp.oAs.pre.ala <- muSDGen(s= n.ala13,                      # oAs BC
                              r= dup.ala13,
                              mu= oas.pre.mu.ala13,
                              sd= oas.pre.sd.ala13)
  temp.oBC.ala <- muSDGen(s= n.ala13,                      
                          r= dup.ala13,
                          mu=obc.mu.ala13,
                          sd=obc.sd.ala13)
  temp.oBC.ala[temp.oBC.ala > upper.ala] <- upper.ala          # oBC truncation
  temp.oBC.ala[temp.oBC.ala < lower.ala] <- lower.ala
  sim.obc.ala13[i,] <- temp.oBC.ala
  
  temp.oAs.post.ala <- temp.oAs.pre.ala * temp.oBC.ala         # oAs post = oBC * oAs pre
  
  temp.tAs.post.ala <- temp.iAs.post.ala + temp.oAs.post.ala   # tAs post * iAs post + oAs post
  temp.tAs.pre.ala <- muSDGen(s= n.ala13,                        # tAs pre
                              r= dup.ala13,
                              mu=tas.pre.mu.ala13,
                              sd=tas.pre.sd.ala13)
  temp.tBC.ala <- temp.tAs.post.ala / temp.tAs.pre.ala          # tAs BC=tAs post / tAs pre
  temp.tBC.ala[temp.tBC.ala > upper.ala] <- upper.ala          # tAs BC truncation
  temp.tBC.ala[temp.tBC.ala < lower.ala] <- lower.ala
  sim.tbc.ala13[i,] <- temp.tBC.ala
  
  temp.prp.ala <- temp.iAs.pre.ala / muSDGen(s= n.ala13,                        # iAs prp=iAs pre/tAs pre
                                             r= dup.ala13,
                                             mu=tas.pre.mu.ala13,
                                             sd=tas.pre.sd.ala13)
  sim.prp.ala13[i,] <- temp.prp.ala
}

## ----------
# study 3 Alava 2015

# iAs BC not reported
# iAs BC = (As3+As5 post) / (As3+As5 pre)

nrow.ala15 <- which(ASBC$Ref == "Alava et al. 2015")
alava15 <- ASBC[nrow.ala15,]
n.ala15 <- length(nrow.ala15)
dup.ala15 <- alava15$replicate

as3.pre.mu.ala15 <- alava15$`AsIII pre_mean`
as3.pre.sd.ala15 <- alava15$`AsIII pre_sd`
as5.pre.mu.ala15 <- alava15$`AsV pre_mean`
as5.pre.sd.ala15 <- alava15$`AsV pre_sd`
oas.pre.mu.ala15 <- alava15$`oAs pre_mean`
oas.pre.sd.ala15 <- alava15$`oAs pre_sd`
tas.pre.mu.ala15 <- alava15$`tAs pre_mean`
tas.pre.sd.ala15 <- alava15$`tAs pre_sd`
as5.post.mu.ala15 <- alava15$`AsV post_mean`
as5.post.sd.ala15 <- alava15$`AsV post_sd`
oas.post.mu.ala15 <- alava15$`oAs post_mean`
oas.post.sd.ala15 <- alava15$`oAs post_sd`
tas.post.mu.ala15 <- alava15$`tAs post_mean`

sim.ias.pre.ala15 <- matrix(NA,iter,sum(dup.ala15))
sim.ibc.ala15 <- matrix(NA,iter,sum(dup.ala15))
sim.obc.ala15 <- matrix(NA,iter,sum(dup.ala15))
sim.tbc.ala15 <- matrix(NA,iter,sum(dup.ala15))
sim.prp.ala15 <- matrix(NA,iter,sum(dup.ala15))

for(i in 1:iter){
  temp.ias.pre.ala <- muSDGen(n.ala15,                #iAs pre=as3+as5 pre
                              dup.ala15,
                              as3.pre.mu.ala15,
                              as3.pre.sd.ala15)+
                      muSDGen(n.ala15,
                              dup.ala15,
                              as5.pre.mu.ala15,
                              as5.pre.sd.ala15)
  sim.ias.pre.ala15[i,] <- temp.ias.pre.ala
  
  temp.ias.post.ala <-  0 +                          # iAs post = As3 post + As5 post, where As3 = 0
                        muSDGen(n.ala15,
                          dup.ala15,
                          as5.post.mu.ala15,
                          as5.post.sd.ala15)
  temp.ibc.ala <- temp.ias.post.ala / temp.ias.pre.ala # iAs BC = iAs post / iAs pre
  temp.ibc.ala[temp.ibc.ala > upper.ala] <- upper.ala  # iAs BC truncation
  temp.ibc.ala[temp.ibc.ala < lower.ala]<- lower.ala
  sim.ibc.ala15[i,] <- temp.ibc.ala
  
  temp.obc.ala <- muSDGen(n.ala15,                # oAs BC = oAs post / oAs pre
                          dup.ala15,
                          oas.post.mu.ala15,
                          oas.post.sd.ala15)/
    muSDGen(n.ala15,
            dup.ala15,
            oas.pre.mu.ala15,
            oas.pre.sd.ala15)
  temp.obc.ala[temp.obc.ala > upper.ala] <- upper.ala         # oAs BC truncation
  temp.obc.ala[temp.obc.ala < lower.ala] <- lower.ala
  sim.obc.ala15[i,] <- temp.obc.ala
  
  temp.tas.pre.ala <- muSDGen(n.ala15,                 # tAs pre
                              dup.ala15,
                              tas.pre.mu.ala15,
                              tas.pre.sd.ala15)
  temp.prp.ala <- temp.ias.pre.ala / temp.tas.pre.ala  # iAs prp
  sim.prp.ala15[i,] <- temp.prp.ala
  
  temp.tbc.ala <- tas.post.mu.ala15 / temp.tas.pre.ala      # tAs BC = tAs post / tAs pre
  temp.tbc.ala[temp.tbc.ala > upper.ala] <- upper.ala         # oAs BC truncation
  temp.tbc.ala[temp.tbc.ala < lower.ala] <- lower.ala
  sim.tbc.ala15[i,] <- temp.tbc.ala
}

## ----------
## study 4 Du et al. 2019

## iAsBC not reported
## iAsBC = iAs_post / iAs_pre
## no replicate in Du's samples
## use SD values to add variability and uncertainty

nrow.du <- which(ASBC$Ref == "Du et al. 2019")
n.du <- length(nrow.du)
du <- ASBC[nrow.du,]
dup.du <- du$replicate

upper.du <- 0.999999
lower.du <- 0

ias.pre.mu.du <- du$`iAs pre_mean`
oas.pre.mu.du <- du$`oAs pre_mean`
tas.pre.mu.du <- du$`tAs pre_mean`
ias.post.mu.du <- du$`iAs post_mean`
oas.post.mu.du <- du$`oAs post_mean`
tas.post.mu.du <- du$`tAs post_mean`
ias.pre.se.du <- sd(ias.pre.mu.du) / sqrt(sum(dup.du))         # global se used as sample SD for simulation
oas.pre.se.du <- sd(oas.pre.mu.du) / sqrt(sum(dup.du))
tas.pre.se.du <- sd(tas.pre.mu.du) / sqrt(sum(dup.du))
ias.post.se.du <- sd(ias.post.mu.du) / sqrt(sum(dup.du))
oas.post.se.du <- sd(oas.post.mu.du) / sqrt(sum(dup.du))
tas.post.se.du <- sd(tas.post.mu.du) / sqrt(sum(dup.du))

sim.ias.pre.du <- matrix(NA,iter,sum(dup.du))
sim.ibc.du <- matrix(NA,iter,sum(dup.du))
sim.obc.du <- matrix(NA,iter,sum(dup.du))
sim.prp.du <- matrix(NA,iter,sum(dup.du))
sim.tbc.du <- matrix(NA,iter,sum(dup.du))

for(i in 1:iter){
  temp.ias.pre.du <- rnorm(n.du,ias.pre.mu.du,ias.pre.se.du)
  temp.ias.post.du <- rnorm(n.du,ias.post.mu.du,ias.post.se.du)
  temp.oas.pre.du <- rnorm(n.du,oas.pre.mu.du,oas.pre.se.du)
  temp.oas.post.du <- rnorm(n.du,oas.post.mu.du,oas.post.se.du)
  temp.tas.pre.du <- rnorm(n.du,tas.pre.mu.du,tas.pre.se.du)
  temp.tas.post.du <- rnorm(n.du,tas.post.mu.du,tas.post.se.du)
  
  sim.ias.pre.du[i,] <- temp.ias.pre.du
  
  temp.ibc.du <- temp.ias.post.du / temp.ias.pre.du         # iAs BC= iAs post/pre
  temp.ibc.du[temp.ibc.du > upper.du] <- upper.du           # iAs BC truncation
  temp.ibc.du[temp.ibc.du < lower.du] <- lower.du
  sim.ibc.du[i,] <- temp.ibc.du
  sim.prp.du[i,] <- temp.ias.pre.du / temp.tas.pre.du       # iAs prp
  
  temp.obc.du <- temp.oas.post.du / temp.oas.pre.du         # oAs BC= oAs post/pre
  temp.obc.du[temp.obc.du > upper.du] <- upper.du           # oAs BC truncation
  temp.obc.du[temp.obc.du < lower.du] <- lower.du
  sim.obc.du[i,] <- temp.obc.du
  
  temp.tbc.du <- temp.tas.post.du / temp.tas.pre.du         # tAs BC= tAs post/pre
  temp.tbc.du[temp.tbc.du > upper.du] <- upper.du           # tAs BC truncation
  temp.tbc.du[temp.tbc.du < lower.du] <- lower.du
  sim.tbc.du[i,] <- temp.tbc.du
}

## ----------
## study 5 Laparra 2005

## iAsBC not reported
## iAsBC = iAs_post/iAs_pre
## iAs_post=As3_post+As5_post

nrow.lap <- which(ASBC$Ref == "Laparra et al. 2005")
n.lap <- length(nrow.lap)
laparra <- ASBC[nrow.lap,]
dup.lap <- laparra$replicate

ias.pre.mu.lap <- laparra$`iAs pre_mean`
ias.pre.sd.lap <- laparra$`iAs pre_sd`
tas.pre.mu.lap <- laparra$`tAs pre_mean`
tas.pre.sd.lap <- laparra$`tAs pre_sd`
as3.post.mu.lap <- laparra$`AsIII post_mean`
as3.post.sd.lap <- laparra$`AsIII post_sd`
as5.post.mu.lap <- laparra$`AsV post_mean`
as5.post.sd.lap <- laparra$`AsV post_sd`
tas.post.mu.lap <- laparra$`tAs post_mean`
tas.post.sd.lap <- laparra$`tAs post_sd`

upper.lap <- 0.999999
lower.lap <- 0

sim.ias.pre.lap <- matrix(NA,iter,sum(dup.lap))
sim.ibc.lap <- matrix(NA,iter,sum(dup.lap))
sim.prp.lap <- matrix(NA,iter,sum(dup.lap))
sim.tbc.lap <- matrix(NA,iter,sum(dup.lap))
sim.obc.lap <- matrix(NA,iter,sum(dup.lap))

for(i in 1:iter){
  temp.ias.pre.lap <- muSDGen(n.lap,                    # iAs pre
                              dup.lap,
                              ias.pre.mu.lap,
                              ias.pre.sd.lap)
  sim.ias.pre.lap[i,] <- temp.ias.pre.lap
  
  temp.tas.pre.lap <- muSDGen(n.lap,                    # tAs pre
                              dup.lap,
                              tas.pre.mu.lap,
                              tas.pre.sd.lap)
  temp.prp.lap <- temp.ias.pre.lap/temp.tas.pre.lap      # iAs prp
  sim.prp.lap[i,] <- temp.prp.lap
  
  temp.ias.post.lap <- muSDGen(n.lap,                    # iAs post=as3+as5 post
                                dup.lap,
                                as3.post.mu.lap,
                                as3.post.sd.lap)+
    muSDGen(n.lap,
            dup.lap,
            as5.post.mu.lap,
            as5.post.sd.lap)
  temp.ibc.lap <- temp.ias.post.lap/temp.ias.pre.lap     # iAs BC = iAs post/ iAs pre
  temp.ibc.lap[temp.ibc.lap > upper.lap] <- upper.lap    # iAs BC truncation
  temp.ibc.lap[temp.ibc.lap < lower.lap] <- lower.lap
  sim.ibc.lap[i,] <- temp.ibc.lap
  
  temp.tas.post.lap <- muSDGen(n.lap,                    #  tAs post
                         dup.lap,
                         tas.post.mu.lap,
                         tas.post.sd.lap) 
  
  temp.tbc.lap <- temp.tas.post.lap / temp.tas.pre.lap # tAs BC = tAs post/pre
  temp.tbc.lap[temp.tbc.lap > upper.lap] <- upper.lap    # tAs BC truncation
  temp.tbc.lap[temp.tbc.lap < lower.lap] <- lower.lap
  sim.tbc.lap[i,] <- temp.tbc.lap
  
  temp.oas.pre.lap <- temp.tas.pre.lap - temp.ias.pre.lap # oAs pre = tAs pre-iAs pre
  temp.oas.post.lap <- temp.tas.post.lap - temp.ias.post.lap # oAs post = tAs post-iAs post
  temp.obc.lap <- temp.oas.post.lap / temp.oas.pre.lap         # oAs BC = oAs post/pre
  temp.obc.lap[temp.obc.lap > upper.lap] <- upper.lap    # oAs BC truncation
  temp.obc.lap[temp.obc.lap < lower.lap] <- lower.lap
  sim.obc.lap[i,] <- temp.obc.lap
}

## ----------
# study 6 Lee 2018

nrow.lee <- which(ASBC$Ref == "Lee et al. 2018")
n.lee <- length(nrow.lee)
lee <- ASBC[nrow.lee,]
dup.lee <- lee$replicate

ias.pre.mu.lee <- lee$`iAs pre_mean`
ias.pre.sd.lee <- lee$`iAs pre_sd`
oas.pre.mu.lee <- lee$`oAs pre_mean`
oas.pre.sd.lee <- lee$`oAs pre_sd`
tas.pre.mu.lee <- lee$`tAs pre_mean`
tas.pre.sd.lee <- lee$`tAs pre_sd`
ias.post.mu.lee <- lee$`iAs post_mean`
ias.post.sd.lee <- lee$`iAs post_sd`
oas.post.mu.lee <- lee$`oAs post_mean`
oas.post.sd.lee <- lee$`oAs post_sd`
tas.post.mu.lee <- lee$`tAs post_mean`
tas.post.sd.lee <- lee$`tAs post_sd`

upper.lee <- 0.99999
lower.lee <- 0

sim.ias.pre.lee <- matrix(NA,iter,sum(dup.lee))
sim.ibc.lee  <- matrix(NA,iter,sum(dup.lee))
sim.prp.lee  <- matrix(NA,iter,sum(dup.lee))
sim.obc.lee <- matrix(NA,iter,sum(dup.lee))
sim.tbc.lee <- matrix(NA,iter,sum(dup.lee))

for(i in 1:iter){
  temp.ias.pre.lee <- muSDGen(n.lee,                     # iAs pre
                              dup.lee,
                              ias.pre.mu.lee,
                              ias.pre.sd.lee)
  sim.ias.pre.lee[i,] <- temp.ias.pre.lee
  
  temp.ias.post.lee <- muSDGen(n.lee,                      # iAs post
                          dup.lee,
                          ias.post.mu.lee,
                          ias.post.sd.lee) 
  temp.ibc.lee <-  temp.ias.post.lee / temp.ias.pre.lee   # iAs BC = iAs post/pre
  temp.ibc.lee[temp.ibc.lee > upper.lee] <- upper.lee   # iAs BC truncation
  temp.ibc.lee[temp.ibc.lee < lower.lee] <- lower.lee
  sim.ibc.lee[i,] <- temp.ibc.lee
  
  temp.tas.pre.lee <- muSDGen(n.lee,                     # tAs pre
                              dup.lee,
                              tas.pre.mu.lee,
                              tas.pre.sd.lee)
  temp.prp.lee <- temp.ias.pre.lee / temp.tas.pre.lee       # iAs prp = iAs / tAs pre
  sim.prp.lee[i,] <- temp.prp.lee
  
  temp.tas.post.lee <- muSDGen(n.lee,                     # tAs post
                          dup.lee,
                          tas.post.mu.lee,
                          tas.post.sd.lee) 
  temp.tbc.lee <- temp.tas.post.lee / temp.tas.pre.lee   # tAs BC = tAs post/pre
  temp.tbc.lee[temp.tbc.lee > upper.lee] <- upper.lee   # tAs BC truncation
  temp.tbc.lee[temp.tbc.lee < lower.lee] <- lower.lee
  sim.tbc.lee[i,] <- temp.tbc.lee
  
  temp.obc.lee <-  (temp.tas.post.lee- temp.ias.post.lee)/  # oAs BC = (tAs - iAs post) / oAs pre
    muSDGen(n.lee,                    
            dup.lee,
            oas.pre.mu.lee,
            oas.pre.sd.lee)
  temp.obc.lee[temp.obc.lee > upper.lee] <- upper.lee   # oAs BC truncation
  temp.obc.lee[temp.obc.lee < lower.lee] <- lower.lee
  sim.obc.lee[i,] <- temp.obc.lee
}

## ----------
# study 7 Mantha et al. 2017

## iAs BC not reported
## iAs BC = iAs post/iAs pre

nrow.man <- which(ASBC$Ref == "Mantha et al. 2017")
n.man <- length(nrow.man)
mantha <- ASBC[nrow.man,]
dup.man <- mantha$replicate

ias.pre.mu.man <- mantha$`iAs pre_mean`
ias.pre.sd.man <- mantha$`iAs pre_sd`
oas.pre.mu.man <- mantha$`oAs pre_mean`
oas.pre.sd.man <- mantha$`oAs pre_sd`
tas.pre.mu.man <- mantha$`tAs pre_mean`
tas.pre.sd.man <- mantha$`tAs pre_sd`
ias.post.mu.man <- mantha$`iAs post_mean`
ias.post.sd.man <- mantha$`iAs post_sd`
oas.post.mu.man <- mantha$`oAs post_mean`
oas.post.sd.man <- mantha$`oAs post_sd`
tas.post.mu.man <- mantha$`tAs post_mean`
tas.post.sd.man <- mantha$`tAs post_sd`

sim.ias.pre.man <- matrix(NA,iter,sum(dup.man))
sim.ibc.man <- matrix(NA,iter,sum(dup.man))
sim.prp.man <- matrix(NA,iter,sum(dup.man))
sim.tbc.man <- matrix(NA,iter,sum(dup.man))
sim.obc.man <- matrix(NA,iter,sum(dup.man))

upper.man <- 0.999999
lower.man <- 0

for(i in 1:iter){
  temp.ias.pre.man <- muSDGen(n.man,                   # iAs pre
                              dup.man,
                              ias.pre.mu.man,
                              ias.pre.sd.man)
  sim.ias.pre.man[i,] <- temp.ias.pre.man
  
  temp.ibc.man <- muSDGen(n.man,                   # iAs BC=iAs post/pre
                          dup.man,
                          ias.post.mu.man,
                          ias.post.sd.man) / temp.ias.pre.man
  temp.ibc.man[temp.ibc.man > upper.man] <- upper.man
  temp.ibc.man[temp.ibc.man < lower.man] <- lower.man
  
  sim.ibc.man[i,] <- temp.ibc.man
  
  temp.tas.pre.man <- muSDGen(n.man,                   # tAs pre
                              dup.man,
                              tas.pre.mu.man,
                              tas.pre.sd.man)
  temp.prp.man <- temp.ias.pre.man / temp.tas.pre.man   # prp = iAs/tAs pre
  sim.prp.man[i,] <- temp.prp.man
  
  temp.tbc.man <- muSDGen(n.man,                   # tAs BC= tAs post/pre
                          dup.man,
                          tas.post.mu.man,
                          tas.post.sd.man) / temp.tas.pre.man
  temp.tbc.man[temp.tbc.man > upper.man] <- upper.man
  temp.tbc.man[temp.tbc.man < lower.man] <- lower.man
  sim.tbc.man[i,] <- temp.tbc.man
  
  temp.obc.man <- muSDGen(n.man,                   # oAs BC= oAs post/pre
                          dup.man,
                          oas.post.mu.man,
                          oas.post.sd.man) / 
    muSDGen(n.man,                   
            dup.man,
            oas.pre.mu.man,
            oas.pre.sd.man)
  temp.obc.man[temp.obc.man > upper.man] <- upper.man
  temp.obc.man[temp.obc.man < lower.man] <- lower.man
  sim.obc.man[i,] <- temp.obc.man
}

## ----------
## study 8 Tokalioglu 2020

nrow.tok <- which(ASBC$Ref == "Tokalioglu et al. 2020")
n.tok <- length(nrow.tok)
toka <- ASBC[nrow.tok,]
dup.tok <- toka$replicate

as3.pre.mu.tok <- toka$`AsIII pre_mean`
as3.pre.sd.tok <- toka$`AsIII pre_sd`
as5.pre.mu.tok <- toka$`AsV pre_mean`
as5.pre.sd.tok <- toka$`AsV pre_sd`
oas.pre.mu.tok <- toka$`oAs pre_mean`
oas.pre.sd.tok <- toka$`oAs pre_sd`
as3.post.mu.tok <- toka$`AsIII post_mean`
as3.post.sd.tok <- toka$`AsIII post_sd`
as5.post.mu.tok <- toka$`AsV post_mean`
as5.post.sd.tok <- toka$`AsV post_sd`
oas.post.mu.tok <- toka$`oAs post_mean`
oas.post.sd.tok <- toka$`oAs post_sd`

upper.tok <- 0.999999
lower.tok <- 0

sim.ias.pre.tok <- matrix(NA,iter,sum(dup.tok))
sim.ibc.tok <- matrix(NA,iter,sum(dup.tok))
sim.prp.tok <- matrix(NA,iter,sum(dup.tok))
sim.tbc.tok <- matrix(NA,iter,sum(dup.tok))
sim.obc.tok <- matrix(NA,iter,sum(dup.tok))

for(i in 1:iter) {
  temp.ias.pre.tok <- muSDGen(n.tok,                 ## iAs pre= As3+As5 pre
                              dup.tok,
                              as3.pre.mu.tok,
                              as3.pre.sd.tok)+
    muSDGen(n.tok,
            dup.tok,
            as5.pre.mu.tok,
            as5.pre.sd.tok)
  sim.ias.pre.tok[i,] <- temp.ias.pre.tok
  
  temp.ias.post.tok <- muSDGen(n.tok,                 ## iAs post= As3+As5 post
                              dup.tok,
                              as3.post.mu.tok,
                              as3.post.sd.tok)+
    muSDGen(n.tok,
            dup.tok,
            as5.post.mu.tok,
            as5.post.sd.tok)
  
  temp.ibc.tok <- temp.ias.post.tok/temp.ias.pre.tok   ## iAs BC= iAs post/pre
  temp.ibc.tok[temp.ibc.tok > upper.tok] <- upper.tok   # iAs BC truncation
  temp.ibc.tok[temp.ibc.tok < lower.tok] <- lower.tok
  sim.ibc.tok[i,] <- temp.ibc.tok
  
  temp.oas.pre.tok <- muSDGen(n.tok,                  ## oAs pre
                              dup.tok,
                              oas.pre.mu.tok,
                              oas.pre.sd.tok)
  temp.oas.post.tok <- muSDGen(n.tok,                  ## oAs post
                               dup.tok,
                               oas.post.mu.tok,
                               oas.post.sd.tok)
  

  
  temp.obc.tok <- temp.oas.post.tok/temp.oas.pre.tok   ## oAs BC= oAs post/pre
  temp.obc.tok[temp.obc.tok > upper.tok] <- upper.tok
  temp.obc.tok[temp.obc.tok < lower.tok] <- lower.tok
  sim.obc.tok[i,] <- temp.obc.tok
  
  temp.tas.pre.tok <- temp.ias.pre.tok+ temp.oas.pre.tok ## tAs pre= iAs+oAs pre
  temp.tas.post.tok <- temp.ias.post.tok+ temp.oas.post.tok ## tAs pre= iAs+oAs pre
  temp.tbc.tok <- temp.tas.post.tok / temp.tas.pre.tok     ## tAs BC = tAs post / pre
  temp.tbc.tok[temp.tbc.tok > upper.tok] <- upper.tok
  temp.tbc.tok[temp.tbc.tok < lower.tok] <- lower.tok
  sim.tbc.tok[i,] <- temp.tbc.tok
  
  temp.prp.tok <- temp.ias.pre.tok / temp.tas.pre.tok  ## prp = iAs/tAs pre
  sim.prp.tok[i,] <- temp.prp.tok
}

## -------------------
all.ibc.mtx <- cbind(sim.ibc.ack,
                    sim.ibc.ala13,
                    sim.ibc.ala15,
                    sim.ibc.du,
                    sim.ibc.lap,
                    sim.ibc.lee,
                    sim.ibc.man,
                    sim.ibc.tok)

```

***

# 2 Parameter estimation   

## 2.1 Empirical distribution   

Based on the simulated data, the empiricial distribution is illustrated in the following histogram:   
```{r} 
hist(apply(all.ibc.mtx,2,median),breaks = seq(from=0,to=1,by=0.1),density = T,freq = F,col = "black")
```

One highlight in the histogram, is the chunck of data at the upper end near the limit of 1. Three studies, Laparra 2005, Ackerman 2005 and Lee 2018, reported a considerable amount of BC >=1.The three studies contributed ~40% of data points. This has significant impact on the estimated parameters.   

## 2.2 ML estimate of beta distribution

I present the ML estimate of beta distribution based on the 1000 iters here.   

```{r}
library(fitdistrplus)

beta.mle <- matrix(NA,iter,2)
for(i in 1:iter){                                                              ## beta by mle
  beta.mle[i,] <- fitdist(all.ibc.mtx[i,],"beta",
                          method = "mle")$estimate
}
  
curve(dbeta(x,beta.mle[1,1],beta.mle[1,2]),col="gray")
for(i in 2:iter){
    
  curve(dbeta(x,beta.mle[i,1],beta.mle[i,2]),add = T,col="gray")
}
```

Before I explain the results,   
1. There is no problem with this package I used. Estimates computed using package is the same as the results by other packages in R, namely EnvStats and MASS.   
2. I further confirmed that the ML estimate of beta by SAS and SPSS are the same as the ones I have here. Those programs does not depend on coding as much as R so there is no way I can make coding mistakes in those programs. It is, therefore, very unlikely that all the ML estimates I have, including those produced by SPSS, are all wrong due to my coding mistakes. 

Now look at the fitting results. 
1. The NaNs are the consequences of the chuck of data near 1,as what I mentioned in section 2.1    
2. For the same reason, the ML estimates of 975/1000 iters have the scale parameter to be smaller than 1. The rest 25 iter have their estimates with a scale parameter >=1 and hence a closed curve.   
3. I have shown a similar figure to you in March. You were not satisfied with the open curve which lead to your command for me to use CrystalBall. The three studies (section 2.1) are still included so this pattern of curves are expected in the current ML estimates.    
4. This also explains why such a beta estimate is considered as poor fit by KS statistics. KS statstics measures the distances between the empirical distribution and theortical distribution. At the upper end near 1, the distances between Inf (theortical) and the empirical density are larger than other distributiosn with closed curves. 

## 2.3 Alternative estimation strageties

If you are not satisfied by the open-form curve as you were in March, here I present the Method of Moment/ Moment Match (MOM) estimates of beta. It has a closed-form curve as the following:
```{r}

beta.mme <- matrix(NA,iter,2)

for(i in 1:iter){                                                              ## beta by mme
  beta.mme[i,] <- fitdist(all.ibc.mtx[i,],"beta",
                          method = "mme")$estimate

}
  curve(dbeta(x,beta.mme[1,1],beta.mme[1,2]),col="gray")
for(i in 2:iter){
    curve(dbeta(x,beta.mme[i,1],beta.mme[i,2]),add = T,col="gray")
}
```

Looking at the results by MME:
1. the NaNs are still here as the data are unchanged   
2. The parameters are estimated by matching the first and second moment (mean and variance) between the empirical and theortical distribution   
3. the curve now has a closed form, as the scale parameters of all iters are now > 1   

# 3 My proposals for getting this done

As mentioned in your email, all the distributions whose domain exceed the interval [0,1] cannot be supported by the bioaccessibility data. As such, only distributions with bounded domain should be considered as candidate models, such as beta, uniform and triangular. 
Furthermore, uniform and triangular seems apprarently poorer than beta as the two distributions are much less flexible. Hence, I believe it is reasonable to argue that *the only reasonalbe candidate model is the beta distribution* and there is no need for model selection. If this would be the case, then this work can be simply completed by providing a MOM estimate of beta parameters. 

I understand your suggestion that it is better to avoid complicated stats so using MME may become an issue. If this is the case, we will need to go back to mle. In our previous discussion, you explained to me why not to do a truncated distribution. I absolutely agree with you that the truncated distributions are hard to comprehend and difficult in application, which hampers the likelihood for our manuscript to be published. However, I think you did not explain to me if truncated distributions are scientifically invalid for our data. I would beg you, if you have time, to enlighten me on this matter.